### 2020-03-12 Writing/disparity_review.tex
Updated refs + compiler

\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia;
$^2$Department of Life Sciences, Natural History Museum, London, Cromwell Road, London, SW7 5BD, UK;
$^{3}$School of GeoSciences, University of Edinburgh, Grant Institute, Edinburgh EH9 3FE, UK;
$^{4}$Department of Biology, University of York, YO10 5DD, UK;
$^{5}$Department of Zoology, School of Natural Sciences, Trinity College, Ireland;
$^{6}$Institut de Syst\'{e}matique, \'{E}volution, Biodiversit\'{e} (ISYEB), Muséum national d'Histoire naturelle, CNRS, Sorbonne Universit\'{e}, EPHE, Université des Antilles, 57 rue Cuvier CP39, 75005 Paris, France;
$^{7}$Ryan Institute, School of Natural Sciences, National University of Ireland Galway, Ireland;
$^{8}$ Division of Paleontology, American Museum of Natural History, New York, USA;
$^{10}$School of Earth and Environment, University of Leeds, Leeds LS2 9JT, UK;
$^{11}$School of Earth Sciences, University of Bristol, Life Sciences Building, Tyndall Avenue, Bristol BS8 1TQ, UK;
$^{12}$Milner Centre for Evolution, University of Bath, BA2 7AY UK;
$^{13}$Department of Earth Sciences, University of Oxford, S Parks Road, Oxford OX1 3AN, UK;
$^{14}$School of Biological Sciences, The University of Adelaide, Adelaide, South Australia 5005, Australia.
$^{15}$ Department of the Geophysical Sciences, University of Chicago, Chicago, Illinois 60637;
$^{16}$ Department of Animal and Plant Sciences, The University of Sheffield, Sheffield S10 2TN, UK;\\
$^{+}$ These authors contributed equally to the manuscript; $^{*}$ Corresponding author: guillert@tcd.ie\\}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/figure_space.pdf}
\caption{
    \tiny{
    Morphospaces: different mathematical representations of a morphospace.
    A trait matrix can be transformed into a distance matrix \citep[e.g in][]{Close2015} or an ordinated matrix \citep[e.g. in][]{tyler2011detecting}.
    Here we consider all these matrices as being \textit{morphospaces}, i.e. objects containing all the combinations of traits and observations (albeit transformed differently).
    Visualisation: different  ways to represent the morphospace in 2D.
    Visualisations can use either trait plots (directly from the trait matrix); ``flattening'' ordination of the data (e.g. using non-metric multidimensional scaling forcing the dataset into two dimensions - note that variance is lost due to the distortion stress and non-metric properties of the resulting operation); or ordination axis plots (directly from the ordinated matrix).
    Note that in 2D representations, it is good practice to plot both axes on the same scale to avoid visually distorting the importance of one axis).
    }
    % @@@ Change references
}
\label{Fig:morphospace}
\end{figure}

>>>>

\noindent { \it 
$^1$ School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia;
$^2$ Department of Life Sciences, Natural History Museum, London, Cromwell Road, London, SW7 5BD, UK;
$^{3}$ School of GeoSciences, University of Edinburgh, Grant Institute, Edinburgh EH9 3FE, UK;
$^{4}$ Department of Biology, University of York, YO10 5DD, UK;
$^{5}$ Department of Zoology, School of Natural Sciences, Trinity College, Ireland;
$^{6}$ Institut de Syst\'{e}matique, \'{E}volution, Biodiversit\'{e} (ISYEB), Muséum national d'Histoire naturelle, CNRS, Sorbonne Universit\'{e}, EPHE, Université des Antilles, 57 rue Cuvier CP39, 75005 Paris, France;
$^{7}$ Ryan Institute, School of Natural Sciences, National University of Ireland Galway, Ireland;
$^{8}$ Division of Paleontology, American Museum of Natural History, New York, USA;
$^{9}$ Department of Cell and Developmental Biology, University College London, London, UK;
$^{10}$ School of Earth and Environment, University of Leeds, Leeds LS2 9JT, UK;
$^{11}$ School of Earth Sciences, University of Bristol, Life Sciences Building, Tyndall Avenue, Bristol BS8 1TQ, UK;
$^{12}$ Milner Centre for Evolution, University of Bath, BA2 7AY UK;
$^{13}$ Department of Earth Sciences, University of Oxford, S Parks Road, Oxford OX1 3AN, UK;
$^{14}$ School of Biological Sciences, The University of Adelaide, Adelaide, South Australia 5005, Australia.
$^{15}$ Department of the Geophysical Sciences, University of Chicago, Chicago, Illinois 60637;
$^{16}$ Department of Animal and Plant Sciences, The University of Sheffield, Sheffield S10 2TN, UK;\\
$^{+}$ These authors contributed equally to the manuscript; $^{*}$ Corresponding author: guillert@tcd.ie\\}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/figure_space.pdf}
\caption{
    \tiny{
    Morphospaces: different mathematical representations of a morphospace.
    A trait matrix can be transformed into a distance matrix \citep[e.g in][]{Close2015} or an ordinated matrix \citep[e.g. in][]{tyler2011detecting}.
    Here we consider all these matrices as being \textit{morphospaces}, i.e. objects containing all the combinations of traits and observations (albeit transformed differently).
    Visualisation: different  ways to represent the morphospace in 2D.
    Visualisations can use either trait plots (directly from the trait matrix); ``flattening'' ordination of the data (e.g. using non-metric multidimensional scaling forcing the dataset into two dimensions - note that variance is lost due to the distortion stress and non-metric properties of the resulting operation); or ordination axis plots (directly from the ordinated matrix).
    Note that in 2D representations, it is good practice to plot both axes on the same scale to avoid visually distorting the importance of one axis).
    }
}
\label{Fig:morphospace}
\end{figure}
